\documentclass[11pt]{article}
\usepackage[margin=1cm]{geometry} 
\usepackage{graphicx}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}

\title{
    \textbf{DBMS 2 Project} \\ 
    \textbf{Group 9 : Weekly Report} \\
}

\author{
    \begin{tabular}{c}
        \textbf{Darpan Gaur} \\
        \textbf{CO21BTECH11004}
    \end{tabular}
    \begin{tabular}{c}
        \textbf{Abhinav Kompella} \\
        \textbf{ES21BTECH11002}
    \end{tabular}
    \begin{tabular}{c}
        \textbf{Aditya Bacharwar} \\
        \textbf{ES21BTECH11003}
    \end{tabular}
    \begin{tabular}{c}
        \textbf{Avaneesh Radhakrishnan} \\
        \textbf{ES21BTECH11022}
    \end{tabular}
}


\date{}

\begin{document}
\maketitle

\hrulefill

\section*{Week 1 [Mar 3 - Mar 7]}
\begin{itemize}
    \item Database design: Discussed the requirements for the project and decided tables, schema, and relationships.  
    \item ER diagram: Created rough ER diagram for the database, need to refine it further.
    \item Technology stack: Decided to use Django as the backend framework, PostgreSQL as the database, and templates (HTML, CSS, JS) from django for the frontend. 
    \item Setup: Installed Django and configure Django with virtual environemnt. Installed PostgreSQL, and pgAdmin on our local machines.
    \item Repository: Created a repository on GitHub do the initial setup and push the code.
\end{itemize}

\section*{Week 2 [Mar 17 - Mar 21]}
\begin{itemize}
    \item Finalized the relations and schema for the database. Noted the functional dependencies and constraints.
    \item Database setup: Created the database and tables in PostgreSQL. Inserted some dummy data to test the API. 
    \item Backend setup: Created the Django project and app. Created the models for the database tables. Created the API for the database.
    \item RBAC: Implemented Role Based Access Control for the API. Created roles for admin, user, and guest.
    \item Authentication: Implemented authentication for the API. Created login, signup, and logout API.
    \item Querying: Implemented querying for the API. Created add, edit, delete, and get API for the database.
\end{itemize}

\section*{Week 3 [Mar 24 - Mar 28]}
% frontend and backend integration, testing
\begin{itemize}
    \item Frontend setup: Created the templates for the frontend. Created the login, signup, home, profile, search, add, edit, delete, logout, and about pages.
    \item Integration: Connected the frontend to the backend. Tested the API with the frontend.
    \item Filtering: Implemented filtering for the API. Created search API for the database.
    \item Testing: Tested the application for bugs and errors. Fixed the some critical bugs and errors.
    \item Documentation: Wrote the documentation for the project.
    \item Iterated the design: Refactored the code and design for better performance and user experience.
\end{itemize}

\end{document}